Supporting Ecological Decision Making Using Feature-Selection and Variable Importance

### 2019-09-01 code/98-paper/ieee/performance-best-per-learner.tex
optimize table best perf per learner

% latex table generated in R 3.5.2 by xtable 1.8-3 package
% Sat Aug 31 23:13:02 2019
\begin{table}[ht]
\centering
\begin{tabular}{rllllr}
  \hline
 & Task & Learner ID & Learner Group & Filter & RMSE \\ 
  \hline
1 & defoliation-all-plots-NRI & RF Car & RF & Car & 33.96 \\ 
  2 & defoliation-all-plots-NRI & Ridge-CV & Ridge-CV & No Filter & 33.98 \\ 
  3 & defoliation-all-plots-HR-VI & SVM Borda & SVM & Borda & 34.25 \\ 
  4 & defoliation-all-plots-HR & Lasso-CV & Lasso-CV & No Filter & 50.45 \\ 
  5 & defoliation-all-plots-HR-VI & Ridge-MBO & Ridge-MBO & No Filter & 58.56 \\ 
  6 & defoliation-all-plots-HR & Lasso-MBO & Lasso-MBO & No Filter & 58.56 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

% latex table generated in R 3.5.2 by xtable 1.8-3 package
% Sun Sep  1 10:28:46 2019
\begin{table}[h!]
\centering
\caption{Best performance of each learner across any task and filter method.} 
\label{tab:best-learner-perf}
\begin{tabular}{rlllr}
  \hline
 & Task & Learner Group & Filter & RMSE \\ 
  \hline
1 & defoliation-all-plots-NRI & RF & Car & 33.96 \\ 
  2 & defoliation-all-plots-NRI & Ridge-CV & No Filter & 33.98 \\ 
  3 & defoliation-all-plots-HR-VI & SVM & Borda & 34.25 \\ 
  4 & defoliation-all-plots-HR & Lasso-CV & No Filter & 50.45 \\ 
  5 & defoliation-all-plots-HR-VI & Ridge-MBO & No Filter & 58.56 \\ 
  6 & defoliation-all-plots-HR & Lasso-MBO & No Filter & 58.56 \\ 
   \hline
\end{tabular}
\end{table}
